\paragraph{Luigi}

As a combo-heavy character, Meta Knights can struggle dealing with Luigi due to having invincibility in the first 7 frames of \textbf{Luigi Cyclone} (Aerial). In order to deal with this, it is necessary to only do \textit{true combos} or bait out the cyclone in advance.

\subparagraph{Combos}
At 0\% falling (shorthop) \textit{nair} provides a lot of good options:
\[
	nair_{shf} \to \begin{cases}
	nair_{bff} \to dtilt \ (*)	\\	
	dtilt	\\
	dmash \ (*)	\\
	dash 
	\begin{cases}
		usmash	\\
		grab	\\
		attack	\\
	\end{cases}
	\end{cases}
\]
The cases marked with $(*)$ deal approximately 23\%, and as such, can set up for better combos which are led by the more usual starters of \textit{dash attack} and \textit{dair}. Dash-grab into up-throw is also a valid contender for this 23\% number. 

Sadly at 23\%, \textit{down air} does not follow true on Luigi. It is first at $26.9\%$, that it can combo into itself. Before this, you can still do $dair \to grab$, which is beaten by spotdodge, which in turn is beaten by another $dair$.

Bear in mind, even at $27\%$, a \textit{shorthop dair} may not be advantageous enough until the minimum $27.8\%$, assuming zero staleness.

At $40\%$ on the top platform of \textbf{Yoshi's Story}, you can drop down and then ladder Luigi to death, if there is imperfect SDI in the perfect direction \textbf{(down and away)} with DI out. The combo itself is a bit infeasible because when both stand on the platform, and Meta Knight gets to do a \textit{dropdown doublejump uair}. Theoretically it could be done against a standing Luigi grab.