\paragraph{Steve}

It might be important for Meta Knights to know how to play against Steve.

\subparagraph{Neutral}
While ahead, Meta Knight usually likes to $dair$-camp, but against Steve, this is not beneficial. Steve obtains resources with his neutral special $mine$, so Meta Knight is forced to play more of a rushdown style than the usual, optimal style of bait-and-punish.

\subparagraph{Interactions}

Steve's \textbf{Minecart} is one of his most annoying moves. Against riding cart, \textit{Mach Tornado} and \textit{Nair} often beat out, or at least, tend to trade with it. \textit{Dsmash} will always beat it out, but requires somewhat tight timing.

Since \textit{minecart} has variable damage depending on its velocity, it can be tough to gauge. But if we assume it to always be \textit{around} 20\%, then all we need to know is that if our damage would exceed 11\%, then it should at least clank.

Crafting Table has \textbf{30 HP}, so to break it, Meta Knight can:
\begin{enumerate}[label = \roman*.]
	\item $dtilt + dsmash_1 + dsmash_2 = 1.2 \times (5 + 10 + 13) = 33.6$
	\item $fsmash + dsmash_2 = 1.2 \times (16 + 13) = 34.8$
	\item $5 \cdot dair = 1.2 \times (5 \times 6) = 36$
\end{enumerate}

\subparagraph{Combos}
\[fair_{f:12[id : 2,3]} \to fsmash\]
Meta Knight's $fair$ serves a potent threat to the floatiness of Steve.
Hitting the second hit of $fair$ allows Meta Knight to $fsmash$ without risk, as he will low-profile all of Steve's aerials. Even though Steve should be able to beat out Meta Knight's $fsmash$ with anything faster than frame 10 - his only real option is to either jump, place TNT, or directional airdodge (as $fair \to fsmash$ beats out neutral airdodge, too). There is a non-zero chance Meta Knight gets hit by Steve $nair$, but this only happens if misspaced.

If the Steve displays counterplay to $fair \to fsmash$, landing with the second hit of $fair$ still provides Meta Knight with at least 7, but typically \textbf{14 frames} of hit advantage -- which is enough to combo into an $usmash$, $uair$ or $Shuttle\ Loop$. Essentially, this works both as a combo starter and as a kill confirm against the (disputed) best character in the game.

At earlier percentages, $fair$ may instead lead to ladders or bridges via $uair$.

\subparagraph{Zero to Death}
\[
	FF\ nair \to dash\ grab \to dthrow \to (RAR)\ uair
		\to bridge
		\to finisher
\]